Rusty Linux: Advances in Rust for Linux Kernel Development

### 2024-09-03 paper.tex
Minor edits for camera ready

For the second approach, researchers take a more traditional micro-kernel implementation~\cite{Chen2023-wb, Liang2021-bo}. By pushing most kernel functionality
to user space, the authors limited the surface area that needs to be proved. Chen X et al.~\cite{Chen2023-wb} took
their implementation one step further by formally verifying their new micro-kernel named Atmosphere
by using both the liner type system of Rust in combination with an SMT solver. They were
able to get a 7.5:1 proof-to-code ratio, which is higher than other formerly verified micro-kernels
SeL4 and CeriKOS both have proof code ratios of 19:1 and 20:1, respectively. While this
approach was novel drivers running in userspace are still not formally verified and don't have to be
written in Rust.

>>>>

For the second approach, researchers take a more traditional micro-kernel implementation~\cite{Chen2023-wb, Liang2021-bo}. By pushing most kernel functionality
to user space, the authors limited the surface area that needs to be proved. Chen X et al.~\cite{Chen2023-wb} took
their implementation one step further by formally verifying their new micro-kernel named Atmosphere
by using both the liner type system of Rust in combination with an SMT solver. They were
able to get a 7.5:1 proof-to-code ratio, which is higher than other formerly verified micro-kernels
SeL4 and CeriKOS both of which have proof code ratios of 19:1 and 20:1, respectively. While this
approach was novel, drivers running in userspace are still not formally verified and don't have to be
written in Rust.
